---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PRmixer

<!-- badges: start -->
[![R-CMD-check](https://github.com/flor14/PRmixer/workflows/R-CMD-check/badge.svg)](https://github.com/flor14/PRmixer/actions)
<!-- badges: end -->

The package **P**eer **R**eview **Mixer** (PRMixer) goal is to assign randomly students from one group as reviewers of another group. The function ` PRmixer::assign_reviewers()` considers that: (1) students cannot be assigned as reviewers of their same group, (2) all groups must have reviewers.

## Installation

You can install the released version of PRmixer from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("PRmixer")
```

And the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("flor14/PRmixer")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PRmixer)

## basic example code
assign_reviewer(seed = 2021,
                dataset = PRmixer::students,
                groups_rw = 30,
                reviewers = 4)

```
**Note:** The students names for this example have been created by `randomNames` package.
