---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# PRmixer

<!-- badges: start -->
<!-- badges: end -->

The package **P**eer**R**eview **Mixer** helps to assign randomly students belonging from one group as reviewers of another group. The function ` PRmixer::assign_reviewers()` considers that: (1) Students cannot be assigned as reviewers of the same group, (2) All groups must have reviewers.

## Installation

You can install the released version of PRmixer from [CRAN](https://CRAN.R-project.org) with:

```r
install.packages("PRmixer")
```

And the development version from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("flor14/PRmixer")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(PRmixer)

## basic example code
assign_reviewer(seed = 2021,
                dataset = PRmixer::students,
                groups_rw = 30,
                reviewers = 4)

```
**Note:** The stuedents names for this example has been created by `randomNames` package.
